\textbf{ Interpretable Gaussian Processes for Stellar Variability\\ I: Static Surfaces }

### 2020-12-26 tex/ms.tex
more figs and more text

\begin{figure}[p!]
    \begin{centering}
        \oscaption{calibration_batch_default_1000}{%
        \xxx{TODO: Batch run with $M=1{,}000$.}
        \label{fig:calibration_batch_default_1000}
        }
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Speed tests \xxx{(TODO)}.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}

@@

\appendix

@@

\input{table}

@@

\bibliography{bib}
\end{document}

>>>>

\begin{figure}[p!]
    \begin{centering}
        \includegraphics[width=0.85\linewidth]{figures/calibration_batch_default_1000_corner.png}
        \oscaption{calibration_batch_default_1000}{%
        \xxx{TODO: Batch run with $M=1{,}000$.}
        \label{fig:calibration_batch_default_1000}
        }
    \end{centering}
\end{figure}

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Evaluation time in seconds for a single log-likelihood evaluation
            as a function of the number of points $K$ in each light curve
            when conditioning on a value of the inclination (blue) and when
            marginalizing over the inclination (orange). At $l_\mathrm{max} = 15$,
            computation of the covariance matrix of the GP takes about 10ms
            on a 2018 MacBook Pro. The dashed line shows the asymptotic scaling
            of the algorithm, which is due to the Cholesky factorization and
            solve operations.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}

@@

\bibliography{bib}

@@

\pagebreak
\appendix

\begin{table}[p!]
    \input{table}
\end{table}

@@

\end{document}
